Analysis for Project

### 2021-11-22 analysis/analysis.Rmd
Add sensitivity analysis separating models by current grade groups
I group the results by elementary,  middle, and high school

```{r monoracial-results}
results_monoracial <- map(list(model0, model1, model2, model3, model4),
                          function(x) {
                            marg(x, "race", type="effects", 
                                 vcov_mat=vcovCL(model, cluster=acs$cluster),
                                 at_var_interest=c("White","Black","Indigenous",
                                                   "Asian","Latino"))[[1]][-1,]
                          })

@@

```{r models-by-age, eval=FALSE}
#run separate models by grade groups
model4a <- update(model4, data=subset(acs, as.numeric(current_grade)<=6))
model4b <- update(model4, data=subset(acs, as.numeric(current_grade)>6 &
                                        as.numeric(current_grade)<=9))
model4c <- update(model4, data=subset(acs, as.numeric(current_grade)>=10))

knitreg(list(model4a, model4b, model4c))
```

>>>>

```{r monoracial-results, warning=FALSE}
results_monoracial <- map(list(model0, model1, model2, model3, model4),
                          function(x) {
                            marg(x, "race", type="effects", 
                                 vcov_mat=vcovCL(x, cluster=acs$cluster),
                                 at_var_interest=c("White","Black","Indigenous",
                                                   "Asian","Latino"))[[1]][-1,]
                          })

@@

## Models by grade

I want to separate the results by age more or less, but I cannot take age directly because then some kids cannot logically be behind grade at certain grade levels. For example, if I restrict to 11 or younger, then none of the 5th graders will be behind grade, by design. So, I will restrict by current grade level which indirectly gets at age. I am going to split it by elementary, middle school, and high school.

```{r models-by-grade, warning=FALSE}
#run separate models by grade groups
model4_elem <- update(model4, data=subset(acs, current_grade<="5th"))
model4_middle <- update(model4, data=subset(acs, current_grade>"5th" & 
                                        current_grade<"9th"))
model4_hs <- update(model4, data=subset(acs, current_grade>="9th"))

coef_table_elem <- calculate_marg_means(model4_elem, 
                                        cluster_var=subset(acs, current_grade<="5th")$cluster)
coef_table_middle <- calculate_marg_means(model4_middle,
                                          cluster_var=subset(acs, current_grade>"5th" & 
                                        current_grade<"9th")$cluster)
coef_table_hs <- calculate_marg_means(model4_hs,
                                      cluster_var=subset(acs, current_grade>="9th")$cluster)

coef_table <- coef_table_elem %>%
  mutate(model="elementary")
coef_table <- coef_table_middle %>%
  mutate(model="middle school") %>%
  bind_rows(coef_table)
coef_table <- coef_table_hs %>%
  mutate(model="high school") %>%
  bind_rows(coef_table) %>%
  mutate(model=factor(model, levels=c("elementary","middle school",
                                      "high school")),
         mrace=factor(mrace, levels=c("Black/White",
                                      "Black/Latino",
                                      "Black/Asian",
                                      "Black/Indigenous",
                                      "White/Indigenous",
                                      "White/Latino",
                                      "White/Asian",
                                      "Latino/Asian",
                                      "Indigenous/Latino",
                                      "Indigenous/Asian")))
